An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-06-03 tex/paper.tex
Fixing various details.
- Moran processes
- Data is available
- Mention readthedocs and travis.ci

As stated in the \textbf{Introduction}, one of the main goals of the library is
to allow for the easy contribution of strategies. Doing this requires the
writing of a simple Python class (which can inherit from other predefined
classes). All components of the library are automatically tested using a
combination of unit, property and integration tests, these tests are run as new
features are added to the library to ensure compatibility. Thus, when submitting
a strategy, a simple test is required which ensures the strategy behaves as
expected.
Full contribution guidelines can be found in the documentation.  As an
example, Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source
code for the Grudger strategy as well as its corresponding test.

@@

\begin{description}[noitemsep,topsep=0pt]
    \item[Name:] Zenodo
    \item[Persistent identifier:]
\href{https://zenodo.org/record/45187}{10.5281/zenodo.45187}
    \item[Licence:] MIT
    \item[Publisher:]  Vincent Knight
    \item[Version published:] Axelrod: Alternator Release. v0.0.28
    \item[Date published:] 2016-01-26
\end{description}

@@

In parallel to the Python library, a tournament is being kept up to date that
pits all available strategies against each other. Figure~\ref{fig:tournament}
shows the results from the full tournament which can also be seen (in full
detail) here: \url{http://axelrod-tournament.readthedocs.org/}. Note that to
obtain this tournament requires a simple change of the code shown in
Figure~\ref{fig:demo_tournament_commands}, changing:

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.75\textwidth]{tournament.pdf}
    \caption{Results from the library tournament (2016-03-31)}
    \label{fig:tournament}
\end{figure}

>>>>

As stated in the \textbf{Introduction}, one of the main goals of the library is
to allow for the easy contribution of strategies. Doing this requires the
writing of a simple Python class (which can inherit from other predefined
classes). All components of the library are automatically tested using a
combination of unit, property and integration tests, these tests are run as new
features are added to the library to ensure compatibility (they are also run
automatically using \url{travis-ci.org}). Thus, when submitting a strategy, a
simple test is required which ensures the strategy behaves as expected.  Full
contribution guidelines can be found in the documentation, which is also part of
the library itself and is hosted using \url{readthedocs.org}.  As an example,
Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source code for
the Grudger strategy as well as its corresponding test.

@@

\begin{description}[noitemsep,topsep=0pt]
    \item[Name:] Zenodo
    \item[Persistent identifier:]
\href{https://zenodo.org/record/53982}{10.5281/zenodo.53982}
    \item[Licence:] MIT
    \item[Publisher:]  Vincent Knight
    \item[Version published:] Axelrod: 1.1.1
    \item[Date published:] 2016-06-01
\end{description}

@@

In parallel to the Python library, a tournament is being kept up to date that
pits all available strategies against each other. Figure~\ref{fig:tournament}
shows the results from the full tournament which can also be seen (in full
detail) here: \url{http://axelrod-tournament.readthedocs.org/}. Data sets are
also available showing the plays of every match that takes place. Note that to
obtain this tournament requires a simple change of the code shown in
Figure~\ref{fig:demo_tournament_commands}, changing:

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.75\textwidth]{tournament.pdf}
    \caption{Results from the library tournament (2016-06-01)}
    \label{fig:tournament}
\end{figure}
